Actions are Bad, Mmkay

### 2018-11-26 paper/ms.tex
Add pattern speed updates

>>>>

\appendix \section{Pattern Speed} Our estimation of the pattern speed is very
crude, but throughout the text we have adopted three different speeds in
order to demonstrate that qualitatively our results do not depend on the
precise numerical value of the pattern speed. We identify the spiral arms by
first plotting a $\phi$-$R$ 2D histogram, shown in
Figure~\ref{fig:pattern_speed}. In order to compute $\phi$ and $R$, we use the principal axes from \citep{2018arXiv180610564S}.

\begin{figure}
\includegraphics[width=\columnwidth]{{pattern_speed_by_eye}.png}
\caption{Pattern speed.}
\label{fig:pattern_speed}
\end{figure}
